\documentclass[11pt,a4paper,sans]{moderncv}        

\usepackage{verbatim}
\usepackage[english]{babel}
%\usepackage{hyperref}

\moderncvstyle{casual}                             
\moderncvcolor{blue}                               
%\nopagenumbers{}                                  

\usepackage[utf8]{inputenc}                       
\usepackage[scale=0.75]{geometry}

% personal data
\name{Diego}{Cué Hernández}
\title{Software Engineer}                               
\address{CDMX}{México}
\phone[mobile]{+52~1~5543654629}                   
%\phone[fixed]{+2~(345)~678~901}
%\phone[fax]{+3~(456)~789~012}
\email{diegocuehdz@gmail.com}                            
\homepage{diegocue.com}                     
\social[linkedin]{diegocuehdz}                       
%\social[twitter]{purnenduk90}
\social[github]{diegocuehdz}       
\quote{“Life is what happens to you while you’re
busy making other plans.” John Lennon.} % Quote o la descripcion mia

\begin{document}

%-----       letter       ---------------------------------------------------------
% recipient data
%\recipient{Company Recruitment team}{Company, Inc.\\123 somestreet\\some city}
%\date{January 01, 1984}
%\opening{Dear Sir or Madam,}
%\closing{Yours faithfully,}
%\enclosure[Attached]{curriculum vit\ae{}}        
%\makelettertitle

%Meter el texto y la carta a escribir. 

%\makeletterclosing
%\clearpage

\makecvtitle

\section{Education}
\cventry{2016--}{B.S. in Applied Mathematics}{Instituto Tecnológico Autónomo de México}{}{}{}

\section{Experience}
\subsection{Professional}
\cventry{2016--today}{Senior iOS Developer}{Tr3sco}{CDMX, México}{}{}%\newline{}%
%Achievements:%
%\begin{itemize}%
%\item Update of RPC-DAQ schematic for switched power supply.
%\item Test methodology development for RPC Test-jig, Pin-Assignment for FPGA, and schematic design.
%\item Design of LC ladder based sub-nanosecond stepped electronically controlled delay circuit.
%\end{itemize}}
\cventry{2018--today}{Junior Python Developer}{Tr3sco}{}{}{}
\cventry{2017--today}{Junior Backend Developer (.Net)}{Tr3sco}{}{}{}
\cventry{2012--2016}{Junior iOS Developer}{Tr3sco}{}{}{}

\section{Languages}
\cvitemwithcomment{Spanish}{Native}{}
\cvitemwithcomment{English}{Native and scientific}{CPE-Level C2}
\cvitemwithcomment{French}{Basic}{}


\section{Certifications}
\cventry{April 2020}{Certified Developer Associate}{AWS}{(Currently Studying for the exam)}{}{}
\cventry{May 2015}{Certificate of Proficiency in English (Level C2)}{University of Cambridge}{Credential ID: 155MX0058003}{}{}
\cventry{April 2015}{IB Diploma}{International Baccaleureate Organization}{Credential ID: D0005730097dly939}{}{}
\cventry{Nov 2012}{iOS Development}{Activ Adobe Authorized Training Center
}{}{}{}

\section{Computer skills}
\cvdoubleitem{Languages}{Objective C, C\#, Java, Swift, Javascript} {Databases}{MySQL, SQLite, MongoDB (Mongoose)}
\cvdoubleitem{Design}{Sketch, Photoshop}{Project Managment}{Microsoft Project}
\cvdoubleitem{Version Control}{Git, Bitbucket, Github}{Services and APIs}{AWS, Google Console Platform}


\section{Projects}
\cventry{2020}{El Califa}{Food Delivery}{iOS Developmment \& Project Managment}{\url{https://elcalifa.com.mx/}}{In this project I was in charge of developing and engineering the iOS App of El Califa, which is a famous restaurant of tacos in Mexico City. I was also in charge of coordinating the project with the backend team as well with the Android Team. Part of my role as engineer and project manager included in designing the optimal interfaces for the project needs and passing the requirenments to both teams. This project had modules and integrations with third party APIs like:
\begin{itemize}
    \item OpenPay.- I integrated the Online Payment processor so that the users could tokenize their credit/debit cards. I was also in charge of developing the library to implement a new set of methods that OpenPay had not developed for iOS Api. 
    \item GeoCoding.- Input of user's address and location
    \item Twilio.- The user inputs their mobile phone and it is validated with a SMS to validate what he inputed. 
\end{itemize}}
\cventry{2019}{Arabela Porteo}{Product delivery \& debt collection app}{Web service design, database architecture \& project management}{\url{https://www.arabela.com/mx/}}{In this project we only developed the Android app, the backend and server side functionality was handled by the company that hired us. I designed the web services -Input, Output- which the app was going to use, I also designed the SQLite architecture for the offline fucntionality. Through out the project I was in charge of managing the project using tools to efficiently solve problems that did arise in the process.}
\cventry{2019}{Teikit and Lucky Sushi}{Food Delivery App}{iOS Development \& Project management}{\url{https://www.teikit.mx}}{In this project I developed the iOS app. After carefully designing the solution based on the clients requirements I developed modules like:
\begin{itemize}
    \item Promotions.- NxM, Coupons and Loyalty programme.
    \item GeoCoding.- Input of user's address and location
    \item Tracking.- Notify the user on the status of his delivery
\end{itemize}}
\cventry{2018}{Phillip Morris International's Real time Inventory Tracking}{Object Detection through Neural Networks Solution}{Python Development}{}{We designed the solution to a problem that PMI had in tracking inventory with the retailers. We proposed a real time tracker using Raspberry Pi and Neural Networks to solve this problem. I developed the Convolutional Neural Network to recognize the different SKUs in the picture. The solution was two fold. First, we found the areas of interest with Fast-RCNN. Second, after founding a bounding box with a certain level of confidence we ran a second CNN with the SKUs of the catalogue. We also showed PMI real time analytics like share of shelf, most sold SKUs, etc.}
\cventry{2017}{Diphsa O2}{Analytics app}{iOS Development}{\url{https://www.diphsa.com/}}{In this project we installed sensors in different oxygen machines through out an oxygen plant. After getting the data of the machines in real time, I developed the iOS app which gave the user the ability to see the analytics of the oxygen plant, the user could, as well, visualize in real time the problems that arise in real time.}
\cventry{2016}{Confidenza}{Collective economies app}{iOS Development, Backend Development}{\url{http://web.confidenza.com.mx/}}{In this project, at first,  I developed the iOS app for booking the services of nurses and orderlies for at home care. Inside the iOS app you can book a nurse with specific skills for your specific need. Later, I was in charge of maintaining the backend as well, if a server-side change was needed, I developed it in .NET.}

\section{Extra Curricular}
\cvlistitem{Composed, recorded and published an album with the band Trípoli, album available in streaming platforms. \url{https://open.spotify.com/artist/0UjjvlTE9gzv77bov1U0Ut}}
\cvlistitem{Certified by Centro de Desarrollo Musical in Luthiering \& adjustment of stringed instrumets}

\end{document}