% personal data
\newcommand \FirstName {Diego}
\newcommand \LastName {Cué}
\newcommand \EngineeringTitle {Software Engineer}
\newcommand \Quote {“Life is what happens to you while you’re
busy making other plans.” John Lennon.}
\newcommand \LocationCity {Mexico City}
\newcommand \LocationCountry {Mexico}

% education experience
\newcommand \TitleEducation {Education}
\newcommand \RangeEducationITAM {2016}
\newcommand \DescriptionEducationAppliedMath {B.S. in Applied Mathematics}
\newcommand \DescriptionEducationITAM {at Mexico's Autonomous Institute of Technology}

% professional experience
\newcommand \PExperienceTitle {Experience}
\newcommand \PExperienceSubTitle {Professional}
\newcommand \Today {today}
\newcommand \Tresco {Tr3sco}
\newcommand \ADomicilio {aDomicil.io}
\newcommand \Freelance {Freelance}
\newcommand \TelevisaUnivision {Televisa Univision}

\newcommand \TechLeadMobileAppsRange {September 2023--today}
\newcommand \TechLeadMobileAppsDescription {Tech Lead for Mobile Applications}

\newcommand \PExpArchIOSRange {2020--\break June 2023}
\newcommand \PExpArchIOSDescription {iOS Architect}

\newcommand \PExpSeniorIOSDevRange {2018--\break June 2023}
\newcommand \PExpSeniorIOSDevDescription {Senior iOS Developer}

\newcommand \PExpSeniorNodeDevRange {2020--today}
\newcommand \PExpSeniorNodeDevDescription {Senior Backend Developer (Node)}

\newcommand \PExpJuniorDotNetRange {2017--2019}
\newcommand \PExpJuniorDotNetDescription {Junior Backend Developer (.NET)}

\newcommand \PExpMidIOSDeveloperRange {2015--2018}
\newcommand \PExpMidIOSDeveloperDescription {Mid iOS Developer}

\newcommand \PExpeJuniorIOSDeveloperRange {2012--2015}
\newcommand \PExpeJuniorIOSDeveloperDescription {Junior iOS Developer}



% languages
\newcommand \LanguagesTitle {Languages}

\newcommand \LanguagesSpanishSubTitle {Spanish}
\newcommand \LanguagesSpanishDescription {Native}
\newcommand \LanguagesEnglish {English}
\newcommand \LanguagesEnglishSubTitle {Native and scientific}
\newcommand \LanguagesEnglishCertification {CPE-Level C2}


% certifications
\newcommand \CertificationsTitle {Certifications}

\newcommand \CertificationsTTTProEssentialsRange {January 2023}
\newcommand \CertificationsTTTProEssentialsDescription {TypeScript Pro Essentials Workshop}
\newcommand \CertificationsTTTProEssentialsProvider {TotalTypeScript}
\newcommand \CertificationsTTTProEssentialsCertID {ID: 818eb490-ad05-465d-9565-429b010eb61f}
\newcommand \CertificationsTTTProEssentialsURL {\url{https://res.cloudinary.com/total-typescript/image/upload/v1735894325/certificate/818eb490-ad05-465d-9565-429b010eb61f/typescript-pro-essentials.png}}

\newcommand \CertificationsGraphRange {November 2023}
\newcommand \CertificationsGraphDescription {Graph Developer Associate}
\newcommand \CertificationsGraphProvider {Apollo}
\newcommand \CertificationsGraphCertID {ID: bdc238c6-efeb-4d00-b8fe-3116ce48a05a}
\newcommand \CertificationsGraphURL {\url{https://www.apollographql.com/tutorials/certifications/bdc238c6-efeb-4d00-b8fe-3116ce48a05a}}

\newcommand \CertificationsVersionControlRange {October 2022}
\newcommand \CertificationsVersionControlDescription {Version Control}
\newcommand \CertificationsVersionControlProvider {Meta}
\newcommand \CertificationsVersionControlCertID {ID: YZPF72Q5S2X7}
\newcommand \CertificationsVersionControlURL {\url{https://coursera.org/verify/YZPF72Q5S2X7}}

\newcommand \CertificationsIntroIOSMobileRange {September 2022}
\newcommand \CertificationsIntroIOSMobileDescription {Introduction to iOS Mobile Development}
\newcommand \CertificationsIntroIOSMobileProvider {Meta}
\newcommand \CertificationsIntroIOSMobileCertID {ID: QYLESCQM7V2Y}
\newcommand \CertificationsIntroIOSMobileURL {\url{https://coursera.org/verify/QYLESCQM7V2Y}}

\newcommand \CertificationsProficiencyRange {May 2015}
\newcommand \CertificationsProficiencyDescription {Certificate of Proficiency in English (Level C2)}
\newcommand \CertificationsProficiencyProvider {University of Cambridge}
\newcommand \CertificationsProficiencyCertID {Credential ID: 155MX0058003}
\newcommand \CertificationsProficiencyURL {}

\newcommand \CertificationsDiplomaRange {April 2015}
\newcommand \CertificationsDiplomaDescription {IB Diploma}
\newcommand \CertificationsDiplomaProvider {International Baccaleureate Organization}
\newcommand \CertificationsDiplomaCertID {Credential ID: D0005730097dly939}
\newcommand \CertificationsDiplomaURL {\url{}}

\newcommand \CertificationsActivIOSRange {November 2012}
\newcommand \CertificationsActivIOSDescription {iOS Development}
\newcommand \CertificationsActivProvider {Activ Adobe Authorized Training Center}
\newcommand \CertificationsActivCertID {}
\newcommand \CertificationsActivURL {}


% computer skills
\newcommand \SkillsTitle {Computer Skills}
\newcommand \SkillsLanguagesSubTitle {Languages}
\newcommand \SkillsLanguagesDescription {Swift, Objective-C, Typescript, C\#}
\newcommand \SkillsDatabasesSubTitle {Databases}
\newcommand \SkillsDatabasesDescription {MySQL, MongoDB SQLite, \break Redis}
\newcommand \SkillsDesignSubTitle {Design}
\newcommand \SkillsDesignDescription {Sketch, Photoshop}
\newcommand \SkillsVersionControl {Version control}
\newcommand \SkillsVersionDescription {Git}
\newcommand \SkillsProjectManagementSubTitle {Project managment}
\newcommand \SkillsProjectManagementDescription {Jira, Linear, Microsoft Project}
\newcommand \SkillsCloudComputingTitle {Cloud computing}
\newcommand \SkillsCloudComputingDescription {AWS, GCP}
\newcommand \SkillsAutomatizationSubTitle {Automatization}
\newcommand \SkillsAutomatizationDescription {Fastlane, GithubActions, Jenkins}
\newcommand \SkillsAPIsSubTitle {APIs}
\newcommand \SkillsAPIsDescription {REST, GraphQL}

% Projects
\newcommand \ProjectsTitle {Projects}

\newcommand \ProjectsTUDNRange {2023-today}
\newcommand \ProjectsTUDNTitle {TUDN}
\newcommand \ProjectsTUDNSubTitle {Sport \& Entertainment mobile app}
\newcommand \ProjectsTUDNRole {Tech Lead, Senior iOS Developer \& Lead React Native Developer}
\newcommand \ProjectsTUDNURL {\url{https://tudn.com/}}
\newcommand \ProjectsTUDNDescription {Description
}

\newcommand \ProjectsADomicilioRange {2018-2023}
\newcommand \ProjectsADomicilioTitle {aDomicil.io}
\newcommand \ProjectsADomicilioSubTitle {Private/White label - Food delivery product SaaS}
\newcommand \ProjectsADomicilioRole {iOS Architecture \& Project Management}
\newcommand \ProjectsADomicilioURL {\url{https://adomicil.io/}}
\newcommand \ProjectsADomicilioDescription {In this project I was in charge of developing, architecturing and engineering the iOS Apps of aDomicil.io, which is a product that focuses on handling the delivery channel of restaurants primarily in Mexico City. I was also in charge of coordinating the project development with the backend team as well with the Android Team. Part of my role as engineer and project manager included in designing the optimal interfaces, and data transfer for the project needs and passing the requirements to both teams. This project had modules and integrations with third party APIs like:
\begin{itemize}
    \item Online Payments.- I integrated the Online Payment processors OpenPay, Stripe, EVO Payments and Mercadopago so that the users could tokenize their credit/debit cards. I was also in charge of developing the library to implement a new set of methods that OpenPay had not developed for iOS API. 
    \item GeoCoding.- Input of user's address and location so that the user can order online. 
    \item Loyalty Programmes.- I implemented diverse Loyalty/reward programmes so that the user could redeem benefits after ordering. 
\end{itemize}}

\newcommand \ProjectsDaimlerRange {2019}
\newcommand \ProjectsDaimlerTitle {Daimler/Mercedes Benz}
\newcommand \ProjectsDaimlerSubTitle {Employee car maintenance and vehicle ordering platform}
\newcommand \ProjectsDaimlerRole {Senior iOS Developer}
\newcommand \ProjectsDaimlerURL {\url{https://www.daimler.com.mx/view/index}}
\newcommand \ProjectsDaimlerDescription {In this project I developed the iOS Application for Daimler/Mercedes Benz which helped employees throught out the company manage their car ownership and leasing. This tedious process was done manually and without technology before we developed the technological solution. By doing this digitalization and optimization of their processes' we helped them save valuable time throught out the whole chain of operation of this tasks. This project gave visibility and traceability through out the whole organization which helped in internal and external auditing. The project had modules like:
\begin{itemize}
    \item Security and IAM.- The iOS app had to implement the Local Authentication/Biometric Authentication libraries so that the user had to use it's biometric identification to use the app
    \item Document Handling.- The application included the Documents, Drive and file management functionalities. The user could upload invoices, bills and evidences to help with the chain and management of their vehicles. 
    \item Mobile Iron Security.- The application was subject to security auditing that we had to pass. The app was modified and changed so that it achieved the hightest security standards. 
\end{itemize}
}

\newcommand \ProjectsArabelaRange {2019}
\newcommand \ProjectsArabelaTitle {Arabela Porteo}
\newcommand \ProjectsArabelaSubTitle {Product delivery \& debt collection app}
\newcommand \ProjectsArabelaRole {Web service design, database architecture \& project management}
\newcommand \ProjectsArabelaURL {\url{https://www.arabela.com/}}
\newcommand \ProjectsArabelaDescription {In this project we only developed the Android app, the backend and server side functionality was handled by the company that hired us. I designed the web services -Input, Output- which the app was going to use, I also designed the SQLite architecture for the offline functionality. Through out the project I was in charge of managing the project using tools to efficiently solve problems that did arise in the process.}

\newcommand \ProjectsTeikitRange {2019}
\newcommand \ProjectsTeikitTitle {Teikit and Lucky Sushi}
\newcommand \ProjectsTeikitSubTitle {Food Delivery App}
\newcommand \ProjectsTeikitRole {iOS Development \& Project management}
\newcommand \ProjectsTeikitURL {\url{https://www.teikit.mx}}
\newcommand \ProjectsTeikitDescription {In this project I developed the iOS app. After carefully designing the solution based on the clients requirements I developed modules like:
\begin{itemize}
    \item Promotions.- NxM, Coupons and Loyalty programme.
    \item GeoCoding.- Input of user's address and location
    \item Tracking.- Notify the user on the status of his delivery
\end{itemize}
}

\newcommand \ProjectsRosewoodRange {2018}
\newcommand \ProjectsRosewoodTitle {Ventanas al paraiso/Rosewood's The residences Homeowner}
\newcommand \ProjectsRosewoodSubTitle {Hotel reservation and management}
\newcommand \ProjectsRosewoodRole {iOS Development}
\newcommand \ProjectsRosewoodURL {\url{https://apps.apple.com/mx/app/the-residences-homeowner/id1345738068}}
\newcommand \ProjectsRosewoodDescription {I developed the Apple applications (iPhone and iPad) for Rosewood Hotels, the developed app served the purpose of helping the homeowers, hotel management, and staff in there day to day tasks by digitalizing the whole experience of reserving vacations, requesting services for there homes/rooms and managing the payment of maintenance fees. The modules and functionalities that this app offers are:
\begin{itemize}
    \item Calendar.- The user has complete control of his reservations and availability times in the hotel room and/or properties.
    \item Digital Payments.- The user can choose to pay his programmed charges to a credit card as well as instantly pay it's fees right in the app. 
    \item Real time chat and notification.- The hotel management, the staff, the owners and the guests can be in constant communication with real time chat services and notifications through out the app. 
\end{itemize}
}

\newcommand \ProjectsPMITrackingRange {2018}
\newcommand \ProjectsPMITrackingTitle {Phillip Morris International's Real time Inventory Tracking}
\newcommand \ProjectsPMITrackingSubTitle {Object Detection through Neural Networks Solution}
\newcommand \ProjectsPMITrackingRole {Python Development}
\newcommand \ProjectsPMITrackingURL {}
\newcommand \ProjectsPMITrackingDescription {We designed the solution to a problem that PMI had in tracking inventory with the retailers. We proposed a real time tracker using Raspberry Pi and Neural Networks to solve this problem. I developed the Convolutional Neural Network to recognize the different SKUs in the picture. The solution was two fold. First, we found the areas of interest with Fast-RCNN. Second, after founding a bounding box with a certain level of confidence we ran a second CNN with the SKUs of the catalogue. We also showed PMI real time analytics like share of shelf, most sold SKUs, etc.}

\newcommand \ProjectsDiphsaRange {2017}
\newcommand \ProjectsDiphsaTitle {Diphsa O2}
\newcommand \ProjectsDiphsaSubTitle {Analytics app}
\newcommand \ProjectsDiphsaRole {iOS Development}
\newcommand \ProjectsDiphsaURL {\url{https://www.diphsa.com/}}
\newcommand \ProjectsDiphsaDescription {In this project we installed sensors in different oxygen machines through out an oxygen plant. After getting the data of the machines in real time, I developed the iOS app which gave the user the ability to see the analytics of the oxygen plant, the user could, as well, visualize in real time the problems that arise in real time.}

\newcommand \ProjectsFemsaRange {2017}
\newcommand \ProjectsFemsaTitle {Femsa RM and Femsa CI}
\newcommand \ProjectsFemsaSubTitle {News and media relationships and internal communication platform}
\newcommand \ProjectsFemsaRole {iOS Development}
\newcommand \ProjectsFemsaURL {\url{https://www.femsa.com/es/}}
\newcommand \ProjectsFemsaDescription {I was involved in developing modules and fucntionalities of Femsa's Platforms. Since Femsa is a gigantic company, we developed two platforms for handling communications. 
\begin{itemize}
    \item Femsa RM ("Relación con Medios").- A platform dedicated in handling communication with news and media channels regarding Femsas news and development. 
    \item Femsa CI ("Comunicación Interna").- A secondary platform that supported internal communication taking into account the hierarchichal structure within the company. The users could communicate internally with different functionalities and modules talking into account the hierarchichal structure of the area where they worked.
\end{itemize}
}

\newcommand \ProjectsPMIRutaRange {2016}
\newcommand \ProjectsPMIRutaTitle {Phillip Morris International's Ruta de campeones and Vencedores}
\newcommand \ProjectsPMIRutaSubTitle {Digital Loyalty and Rewards Programme}
\newcommand \ProjectsPMIRutaRole {iOS Development}
\newcommand \ProjectsPMIRutaURL {}
\newcommand \ProjectsPMIRutaDescription {I was in charge of developing PMI's Loyalty Programmes for it's Sellers. PMI had a programme with the convenience stores through out Mexico, if the sellers reached certain metrics and KPIs they would unlock rewards and business opportunities with PMI. Some of the funtionalities that the app included were:
\begin{itemize}
    \item QR Code Scanning and Camera.- The app included scanning of QRcodes, Barcodes and evidence handling. The user had to input data, upload evidence in multipart format and scan information on the go. 
    \item Offline handling.- The app had to work when the user was offline. Taking into account that the app users could be on the road for hours at a time, at difficult network conditions, the app handled being offline by saving all the data locally until the user had connection and uploaded it. 
\end{itemize}
}

\newcommand \ProjectsConfidenzaRange {2016}
\newcommand \ProjectsConfidenzaTitle {Confidenza}
\newcommand \ProjectsConfidenzaSubTitle {Collective economies app}
\newcommand \ProjectsConfidenzaRole {iOS Development, .NET Development}
\newcommand \ProjectsConfidenzaURL {\url{http://web.confidenza.com.mx/}}
\newcommand \ProjectsConfidenzaDescription {In this project, at first,  I developed the iOS app for booking the services of nurses and orderlies for at home care. Inside the iOS app you can book a nurse with specific skills for your specific need. Later, I was in charge of maintaining the backend as well, if a server-side change was needed, I developed it in ASP .NET.}

\newcommand \ProjectsMVSRange {2015}
\newcommand \ProjectsMVSTitle {MVS Noticias}
\newcommand \ProjectsMVSSubTitle {News, Editorial and Publishing}
\newcommand \ProjectsMVSRole {iOS Development}
\newcommand \ProjectsMVSURL {\url{https://apps.apple.com/us/app/mvs-noticias/id324724789}}
\newcommand \ProjectsMVSDescription {In this app I helped with developing specific modules that would connect with the work of my team mates. I was in charge of developing strategic modules regarding multimedia management so that the user would have a smooth experience when navigating the app. The module that I developed was the podcast and audio player in app. The user could consume the podcast, live stations and audios that were available in the app and do it in a non-invasive way. The user could be reading other news reports and listen to an audio at the same time.}

\newcommand \ProjectsRadioFormulaRange {2015}
\newcommand \ProjectsRadioFormulaTitle {Radio Fórmula}
\newcommand \ProjectsRadioFormulaSubTitle {News, Editorial and Publishing}
\newcommand \ProjectsRadioFormulaRole {iOS Development}
\newcommand \ProjectsRadioFormulaURL {\url{https://www.radioformula.com.mx/temas/app-15254.html}}
\newcommand \ProjectsRadioFormulaDescription {In this app I helped with developing specific modules that would connect with the work of my team members. I was in charge of developing a strategic module regarding multimedia management so that the user would have a smooth experience when navigating the app. The module that I developed was regarding the functionality of video consumption. The user could navigate the app while watching an in picture video in the UI of the app.}

% extra curricular
\newcommand \ExtraCurricularTitle {Extra curricular}
\newcommand \ExtraCurricularTripoli {Composed, recorded and published an album with the band Trípoli, album available in streaming platforms. \url{https://open.spotify.com/artist/0UjjvlTE9gzv77bov1U0Ut}}
\newcommand \ExtraCurricularParaLaMaga {Recorded and published an album for Jordy Ulloa, album available in streaming platforms. \url{https://open.spotify.com/album/2KGPH79cYs69BldZr6DnwS?si=LaJFV1MATVe7SbkXAU9b6A}}
\newcommand \ExtraCurricularLuthier {Certified by Centro de Desarrollo Musical in Luthiering \& adjustment of stringed instrumets}